---
title: 'Time Series Forecast: Amazon'
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r}
#install.packages("pbapply")
library(quantmod)
#install.packages("lubridate")
library(lubridate)
library(xts)
library(zoo)
library(pbapply)

# Define the ticker symbol and download data
getSymbols("AMZN", from = "2000-01-01", to = Sys.Date())

# Use Ad() to get Adjusted closing prices
tmp <- Ad(AMZN)

# Print the adjusted prices
print(tmp)
```

```{r}
# Create a variable to store the returns
rets <- ROC(tmp, type = "discrete")
rets[is.na(rets)] <-0
mean(rets)
sd(rets)
```

```{r}
# Create a formula to return the predicted price
stk_ret = function(STK_PRC, N, MEAN, STDEV)
{
  delta_t = 1/N # for 1 period
  for (i in seq(N))
  {
    epsilon <- runif(n=1, min=0, max=1) # random probabilities
    STK_PRC <- STK_PRC * (1+ qnorm(epsilon, MEAN*delta_t, STDEV*sqrt(delta_t)))
  }
  STK_PRC
}

#latest quote
last(tmp)
```

```{r}
library(lubridate)

#run 1000 simulations
simulations <- 1000

# number of trading days
N = 20 #look back 20 days to predict the stock price, this will be our window

STK_PRC <- as.numeric(coredata(tmp[Sys.Date() - days(20)]))

# Get the mean and the standard deviation of the returns
MEAN = mean(rets)
STDEV = sd(rets)

#Print the results
MEAN
STDEV
```


```{r}
# Create a vector to store stock prices
stock_prices <- c()
for (i in seq(simulations))
{
  stock_prices <- c(stock_prices, stk_ret(STK_PRC = STK_PRC, N=N, MEAN=MEAN, STDEV = STDEV))
}

# Show the predictions
stock_prices
```

```{r}
# Create a summary for the predictions
quantile(stock_prices)
```
#The lowest possible value $157 and highest $192 for today's predictions

```{r}
# Get the actual values
last(tmp)
```
#Because we use the mean and the standard deviation to predict the stock prices our estimates are off. These numbers do not adjust to market trends so it does not capture the volatility and stock price movements which leads to a higher spread between the predictions and the actual stock price. The standard deviation will maintain the prices within the same range. 

```{r}
# Now we are going to calculate the predictions for each month

# we will use options expiration dates
EXPIRY <- tmp[options.expiry(tmp)]
EXPIRY #monthly options expiration date along with the prices
```
```{r}
# Now we will try to predict the option expiration price for each date
EXPIRY <- EXPIRY["2000::"] #EVERYTHING AFTER THE YEAR 2000
IDX <- index(EXPIRY)
NEXT.EXPIRY <- as.Date("2024-02-22")
IDX <- c(IDX, NEXT.EXPIRY)
```

```{r}
# Calculate the mean and stdev for the option prices
MEAN = function(calculateUNTIL) #calculate the mean until a certain date
{
  tmp <- tmp[paste0("::", calculateUNTIL)]
  tmp <- ROC(tmp, type = "discrete")
  tmp[is.na(tmp)]<-0 # if there are any NA's set those to 0
  mean(tmp)
}

STDEV = function(calculateUNTIL) #calculate the mean until a certain date
{
  tmp <- tmp[paste0("::", calculateUNTIL)]
  tmp <- ROC(tmp, type = "discrete")
  tmp[is.na(tmp)]<-0 # if there are any NA's set those to 0
  sd(tmp)
}
```

```{r}
means <- do.call(rbind, lapply(as.list(IDX), MEAN))

stdevs <- do.call(rbind, lapply(as.list(IDX), STDEV))

#CALCULATE THE DIFFERENCE BETWEEN THE DATES OF THE OPTIONS EXPIRATION DATES
days = as.numeric(diff(IDX))
```

```{r}
#Now we will write the Monte Carlo function
MONTE.CARLO = function(sim, iter, LastIter)
{
  simulations <- sim
  N <- days[iter]
  STK_PRC <- as.numeric(EXPIRY[iter])
  MEAN <- means[iter]
  STDEV <- stdevs[iter]
  stock_prices <- c()
  
  for(i in seq(simulations))
  {
    stock_prices <- c(stock_prices, stk_ret(STK_PRC = STK_PRC, N=N, MEAN=MEAN, STDEV = STDEV))
  }
  
  START <- as.data.frame(round(STK_PRC, 2))
  START.DATE = index(EXPIRY[iter])
  PROBS = as.data.frame(t(round(quantile(stock_prices, probs = seq(0,1,0.05)), 2)))
  
  if(iter == LastIter) #if this is the last iteration
  {
    END <- as.data.frame(NA)
    END.DATE = as.data.frame(NA)
  }else{
    END <- as.data.frame(as.numeric(round(EXPIRY[iter+1], 2)))
    END.DATE = index(EXPIRY[iter+1])
  }
  all <- cbind(START, START.DATE, PROBS, END, END.DATE)
  
  #rename columns
  colnames(all) <- c("START.PRC", "START.DATE", "0%", "5%", "10%", "15%",
                     "20%", "25%", "30%", "35%", "40%", "45%", "50%", "55%",
                     "60%", "65%", "70%", "75%", "80%", "85%", "90%", "95%",
                     "100%", "END.PRC", "END.DATE")
  all

}

p <- pblapply(as.list(1:length(days)), function(x){
  MONTE.CARLO(sim=10000,iter = x, LastIter = length(days))
})

p <- do.call(rbind, p)

plot(p$END.PRC, type = "l")
lines(p$`0%`, col = "red")
lines(p$`100%`, col = "green")
```

```{r}
#Number of months
nMo <- nrow(p) #defined by the number of rows

# Number of times it closes above 100% threshold
sum(as.numeric(na.omit(ifelse(p$END.PRC > p$`100%`,1, 0))))/nMo

#Number of times it closes below 0%
sum(as.numeric(na.omit(ifelse(p$END.PRC > p$`0%`,1, 0))))/nMo
```
